Identification of protoneutron star g-modes in gravitational-wave data \pcd{[PCD: alt. title]Inference of proto-neutron star properties from gravitational wave data in core-collapse supernovae.}

### 2020-09-11 appendixA.tex
more updates

\section{G-mode reconstruction}

Given the spectrogram and an specified time interval for the g-mode reconstruction, our proposal method works as follows.  The starting point must be specified.  It can be either at the beginning or at the end of the signal.  Then, in one of these extremes, the maximum energy value is identified, registering its frequency.  This is done independently for a number of consecutive time intervals.  Then we calculate the median of these frequency values, providing a robust starting value for the g-mode reconstruction.

@@

Given the sequence of g-mode estimates, the confidence band will be calculated by using the model defined in \eqref{eq:universal}. The g-mode estimates are frequency values which we use as predictors in the model in order to generate confidence intervals for the ratios. Since the g-mode estimates are indexed by time, the confidence intervals for the ratios are too.  Thus, we generate the confidence band by interpolating the lower and upper limits of the collection of consecutive confidence intervals, which will be valid for the time range of the g-mode estimates.  This confidence band is used to estimate the coverage probabilities in our simulation studies presented below.

>>>>

\section{G-mode reconstruction}
\label{app:gmode}
Given the spectrogram and an specified time interval for the g-mode reconstruction, our proposal method works as follows.  The starting point must be specified.  It can be either at the beginning or at the end of the signal.  Then, in one of these extremes, the maximum energy value is identified, registering its frequency.  This is done independently for a number of consecutive time intervals.  Then we calculate the median of these frequency values, providing a robust starting value for the g-mode reconstruction.

@@

Given the sequence of g-mode estimates, the confidence band will be calculated by using the model defined in \eqref{eq:model1}. The g-mode estimates are frequency values which we use as predictors in the model in order to generate confidence intervals for the ratios. Since the g-mode estimates are indexed by time, the confidence intervals for the ratios are too.  Thus, we generate the confidence band by interpolating the lower and upper limits of the collection of consecutive confidence intervals, which will be valid for the time range of the g-mode estimates.  This confidence band is used to estimate the coverage probabilities in our simulation studies presented below.
